---
title: "Lab 00 - Hello IDS!"
author: "JAMIE BURRELL"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Jamie Burrell", "Charlie Franklin-White", "Dru Keiri", "Sean Wang", 
           "Annie Loi", "Duncan Hoyland"),
  github_username = c("jamie-burrell", "cfranklinwhite", "squarehedge34", 
                      "sw-005", "aaaannniie", "duncan-hoyland"), 
  colour = c("blue", "blue", "purple", 
             "green", "blue", "seagreen"),
  hobby = c("climbing", "poker", "basketball", 
            "gaming", "gaming", "rugby"),
  favourite_number = c(2, 2, 6, 8, 7, 2)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

The bar graph shows the favourite number (on the y-axis) and favourite colour (the bar itself) of each team member according to their GitHub username (on the x-axis).


### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub username", 
          y = "Favourite number",
          title = "Favourite colours and numbers of GitHub users at Table 5")
```

The labs() command allows us to add a title and axis labels to our plot.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

There are so many different hobbies with few individuals doing each meaning that the data is not very informative or easy to interpret and draw conclusions from. To improve the visualisation, hobbies could be grouped into categories, and members could be required to pick from a pre-existing list of categories. In terms of visualisation it could also be plotted as a pie chart to more easily interpret.